%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Chapter:  Arrival
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Arrival}

\info{TODO}

Aapo arrives at a spaceport for a suborbital flight, then arrives at Eliza Central for further education. He sees but does not meet the Education Ecclesical at the greeting ceremony. He begins to learn to think without his slate, but is scheduled to receive his first embed. He is warned that many robotic surgeries will be required to keep up his embed as he grows, but will become progressively less invasive.

\begin{itemize}
\item Additional discussion between senior members regarding the new cohort? (Show, don't tell)
\item Model the senior leadership of Eliza like in Plato's Republic. This includes relationships to children once they have been collected.
\end{itemize}

\info{END TODO}

By morning I felt better. Pilar and Elisa passed out a boxed breakfast that had somehow been warmed. The omelette wasn't bad, but it certainly wasn't fresh. It felt a bit... dead after years of fresh-off-the-farm dunbar food. It left a strange taste in my mouth so I queued for the toilets to clean my teeth and brush my tongue.

Did anyone think Pilar was going to let us rest for the remainder of the drive? She asked us as Alejandro, and I collected the boxes and stacked them in a purpose-built storage container behind the toilets. Nobody answered her rhetorical question. Of course we didn't.

``Qiang, what is virtue?'' An androgynous, diligent-looking student lifted their head. 



% If the chapter ends in an odd page, you may want to skip having the page
%  number in the empty page
\newpage
\thispagestyle{empty}
